### 2016-01-16 04-evaluation.tex
More little textual thingies

The previous sections focused on the computational performance of the
distributed implementation. However, the algorithm's throughput does not
necessarily indicate how fast it can converge to a solution. More specifically, it
remains unclear how many iterations are needed for the algorithm to reach a
stable state and terminate. Therefore, we now shift our focus to the
convergence time to assess the system's utility. Figure~\ref{fig-ppx} presents
the convergence time of the data sets listed in Table~\ref{tab-datasets}.
%
The results in sub-figures a, b and c were obtained by using 64 compute nodes
of DAS5. In Figure~\ref{fig-ppx}-a, the number of communities was set to 12K
which fully occupied the aggregate memory resources of all 64 machines since
com-Friendster has roughly 65 million vertices. In this case, the algorithm
reached a stable state after 3-4 hours. Next, Figures~\ref{fig-ppx}-b and
\ref{fig-ppx}-c present the convergence of com-LiveJournal and com-Orkut
respectively. As the number of vertices in these data sets is an order of
magnitude smaller than com-Friendster, we used a larger number of
communities. Naturally, the convergence time was extended as the complexity of
the algorithm increases dramatically with larger K. However, the system was
capable of reporting results for both in around 40 hours.
%
Figures~\ref{fig-ppx}-d, \ref{fig-ppx}-e and \ref{fig-ppx}-f were all
configured to use the total number of ground-truth communities associated with
their respective data sets, com-Youtube, com-DBLP and com-Amazon. However,
these experiments were conducted on 14, 24 and 24 cluster nodes respectively.

>>>>

The previous sections focused on the computational performance of the
distributed implementation. However, the algorithm's throughput does not
necessarily indicate how fast it can converge to a solution. More specifically, it
remains unclear how many iterations are needed for the algorithm to reach a
stable state and terminate. Therefore, we now shift our focus to the
convergence time to assess the system's utility. Figure~\ref{fig-ppx} presents
the convergence time of the data sets listed in Table~\ref{tab-datasets}.
%
The results in sub-figures a, b and c were obtained by using 65 compute nodes
of DAS5. In Figure~\ref{fig-ppx}-a, the number of communities was set to 12K
which fully occupied the aggregate memory resources of all 64 worker nodes since
com-Friendster has roughly 65 million vertices. In this case, the algorithm
reached a stable state after 3-4 hours. Next, Figures~\ref{fig-ppx}-b and
\ref{fig-ppx}-c present the convergence of com-LiveJournal and com-Orkut
respectively. As the number of vertices in these data sets is an order of
magnitude smaller than com-Friendster, we could use a larger number of
communities to fill up the collective memory. Naturally, the convergence time was extended as the complexity of
the algorithm increases dramatically with larger K. However, the system was
capable of reporting results for both in around 40 hours.
%
Figures~\ref{fig-ppx}-d, \ref{fig-ppx}-e and \ref{fig-ppx}-f were all
configured to use the number of ground-truth communities associated with
their respective data sets, com-Youtube, com-DBLP and com-Amazon. Since this
yields a much smaller storage requirement,
these experiments were conducted on 14, 24 and 24 cluster nodes respectively.
